A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-23 5_generalization.tex
explain how the generalization can be done without extra work

>>>>

Because the peripheral height adjustment was described in terms of a mapping from radial distances to junctions rather than adjusting the heights of peripheral nodes,
we can introduce non-linear mappings without refining the surface mesh.
In the simplified geometrical conceptualization of our technique we can introduce different distributions of bead widths from the center outward, by making the contours of the cones curved.
If the UoC mesh is generated with cones which are curving inward toward the top, higher slicing planes would intersect more sparsely than lower ones, which means that the inter-bead distance and thsu their width becomes larger when going inward.
In order for the simplified geometrical approach to capture such curved shapes it would have to perform mesh refinement.
However, our approach bypasses the peripheral height adjustment and directly generates the radial distances at the slicing heights, which means our technique generalized effortlessly.
